%-------------------------
% Resume in Latex
% Author : Ashish Singh
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[pro]{fontawesome5}

\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[3]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \textit{\footnotesize{#3}}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\name}{Ashish Singh} % Your Name
\newcommand{\course}{Chemical Engineering} % Your Program
\newcommand{\phone}{9320459871} % Your Phone Number
\newcommand{\emaila}{ashishsingh1501@gmail.com} %Email 1

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{tabularx}{\textwidth}{X r}  % X for left-aligned, r for right-aligned
    \textbf{\Huge Ashish Singh}  & \faPhone\ +91-9320459871 \\
      & \faEnvelope\ \href{mailto:ashishsingh1501@gmail.com}{ashishsingh1501@gmail.com} \\
    {Area of Interest} & \faGithub\ \href{https://github.com/morancium}{GitHub Profile} \\
    Technical: \textit{Computer Vision, Generative AI, AI Explainability} & \faLinkedin\ \href{https://www.linkedin.com/in/ashishsingh1501/}{LinkedIn Profile} \\
    Extracurricular: \textit{Badminton, Hiking, Public speaking, Tutoring}
\end{tabularx}
}
\vspace{-5.5 pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Technology, Roorkee}{2020 --2024}
      {Bachelor of Technology in Chemical Engineering}{8.1/10}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Analyst 2 - Data Science }{June 2024- Present}
      {Accordion}{Hyderabad}
      \resumeItemListStart
        \resumeItem{Pioneered geospatial analytics by harnessing satellite imagery, sales trends, and demographic insights to pinpoint high-opportunity regions for solar panel deployment.}
        \resumeItem{Integrated geospatial intelligence into a linear optimization model, identifying 500+ high-potential ZIP codes and driving strategic market expansion.}
        \resumeItem{Implemented data-driven workforce scheduling, boosting installation efficiency by 50\% while cutting costs 40\%}
        \resumeItem{Engineered advanced computer vision solutions (YOLO, Detectron) with semi-supervised learning to enhance solar panel detection, refining market segmentation and targeting accuracy by 34\%.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
   % \resumeSubSubheading
   %  {Software Engineer I}{Oct 2014 - Sep 2016}
   %  \resumeItemListStart
   %     \resumeItem{Apache Beam}
   %       {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
   %  \resumeItemListEnd
   % \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {AI Research Intern - Deepfake Detection}{April 2024 - June 2024}
      {ConTrails.ai}{Remote}
      \resumeItemListStart
        \resumeItem{Designed custom datasets utilizing deepfake generation models, including FaceSwap, LipSync, and Talking Head.}
        \resumeItem{Constructed a preprocessing pipeline that downloaded specific YouTube videos, standardized them to 25 fps, and cropped clips to focus on points of interest (POI).}
        \resumeItem{Created high-fidelity deepfake datasets using FaceFusion, Video Retalking, etc., enhancing model training.}
        \resumeItem{Utilized DeepFakeBench to fine-tune the Xception model, achieving 95\% accuracy on the custom dataset.}
    \resumeItemListEnd

    \resumeSubheading
      {Python and Machine Learning Intern}{December 2023 - February 2024}
      {Swar Yantra Technologies Pvt. Ltd.}{Remote}
      \resumeItemListStart
        \resumeItem{Used open-source LLMs and embedding models from HuggingFace to enhance document analysis capabilities.}
        \resumeItem{Leveraged Language Models for accurate extraction of specific fields from various document types.}
        \resumeItem{Refined prompt engineering techniques, improving document extraction accuracy by 20\%.}
      \resumeItemListEnd

      \resumeSubheading
      {Decision Analytics Intern}{May 2023 - July 2023}
      {EXL Services}{Remote}
      \resumeItemListStart
        \resumeItem{Delivered an automated data extraction pipeline using OCR and Regex, reducing manual processing time by 60\%}
        \resumeItem{Integrated language models to develop personalized expense reports that support natural language querying.}
        \resumeItem{Hosted a web interface to improve user interaction with bank statements, streamlining data analysis processes.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Gen AI-powered Business Development Assistant} $|$  \emph{Generative AI, Python, Streamlit, Faiss, Langchain}}{}
          {AI-powered Business Development Assistant for client insights, case study recommendations, and strategy automation}
          \resumeItemListStart
            \resumeItem{Built AI assistant analyzing 100+ sources to identify client pain points and engagement opportunities.}
            \resumeItem{Developed case study recommendation engine with an active feedback-driven chatbot optimizing solution matching}
            \resumeItem{Systematized PowerPoint reporting tool with Streamlit interface, reducing the manual effort from 40 to 2 hours weekly and automating strategy exports.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{The Vital Extraction Challenge} $|$ \emph{Computer Vision, Python, Pytorch, OpenCV, YOLO, Git}}{}
          {A computer vision model to extract 5+ key vital signs from an image of an ECG monitor in the wild.}
          \resumeItemListStart
            \resumeItem{Secured Silver medal in Inter-IIT Tech Meet 11.0 by achieving 93.26\% accuracy in ECG vital sign extraction.}
            \resumeItem{Utilized advanced models, data augmentation, noise reduction, and semi-supervised learning, optimizing inference speed to 2.3 seconds on Google Colab CPU.}
          \resumeItemListEnd

        \resumeProjectHeading
          {\textbf{Image Colorization Using Conditional GANs} $|$ \emph{Generative AI, Python, Pytorch, FastAPI, COCO dataset}}{}
          {A pipeline for colorizing black-and-white images using deep learning techniques.}
          \resumeItemListStart
            \resumeItem{Developed an automated image colorization model using Conditional GANs based on the Pix2Pix architecture.}
            % \resumeItem{Integrated a pre-trained ResNet18 model as a backbone to enhance feature extraction in PyTorch.}
            \resumeItem{Optimized model performance through adversarial training, data augmentation, and hyperparameter tuning.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, SQL, C/C++, MATLAB, JavaScript} \\
     % \textbf{Frameworks}{: React, Node.js, Flask, JUnit, WordPress, Material-UI, FastAPI} \\
     \textbf{Developer Tools}{: Git, Google APIs, VS Code, PyCharm, Streamlit, CVAT, Roboflow} \\
     \textbf{Libraries}{: PyTorch, Transformers, Tensorflow, Numpy, Scikit-Learn, Regex, Pandas, LangChain} \\
     \textbf{Additional Courses}{: Stanford Online: CS224n, CS229, Statistics 110: Probability, Data Mining for Business Intelligence.}
    }}
 \end{itemize}



 \section{Positions of Responsibility}
 \resumeSubHeadingListStart
     \resumeProjectHeading
       {\textbf{Head, AI/ML Vertical} $|$ \emph{Artificial Intelligence and Electronics Society, IITR}}{May 2023 - May 2024}
       {Headed a 60+ member AI/ML team, driving competition success and hands-on ML project development.}

     \resumeProjectHeading
       {\textbf{UGTA} $|$ \emph{Academic Reinforcement Program}}{Jan 2022 - March 2022}
       {Provided guidance and mentoring to first-year students in MAN001 course}
 \resumeSubHeadingListEnd

\section{Achievements}
 \resumeSubHeadingListStart
     \resumeProjectHeading
       {\textbf{Silver Meda} $|$ \emph{Inter-IIT Tech Meet 11.0}}{2023}
       {Secured 2nd place among 23 IITs in mid-prep PS of Inter-IIT Tech Meet 11.0}

     \resumeProjectHeading
       {\textbf{Gold Medal} $|$ \emph{Integration Bee}}{2023}
       {Secured 1st place among 65 teams in Integration Bee 2023}
     \resumeProjectHeading
       {\textbf{Mentee} $|$ \emph{Amazon ML Summer School}}{2023}
       {Ranked in the top 5\% of Amazon ML Summer School participants}
 \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}